### 2014-12-12 paper.tex
Various fixes, mostly to citations

\usepackage{fancyhdr,hyperref,setspace,booktabs,amsmath,multirow,mathpazo}
\usepackage[pdftex]{graphicx}
\usepackage[margin=1in,includehead]{geometry}

\setcounter{secnumdepth}{0}

@@

  \section{Background}\label{background}

@@

  A given plan has symmetry if "similary-situated parties are treated equally", thus expecting that an even split in votes across two parties would have an even split in seats. Furthermore, if a plaintiff challenging a redistricting plan can demonstrate partisan intent and asymmetry, it would be sufficient for the burden of proof to shift to the state.  Nevertheless, while acknowledging the viability of symmetry as a metric to determine a discriminatory impact on voters, the court failed to establish an accepted standard or test to determine illegal gerrymandering.  Existing measures at the time, as calculated by social scientists, used hypothetical models to predict how election outcomes would turn out, given certain shifts in the electorate and certain vote shares in a given election. The court rejected the notion of using hypothetical models for a standard of constitutionality. \cite{LULAC v. Perry} \\

  With this in mind,  as an alternative to other existing metrics, two legal scholars recently proposed measuring \textit{vote efficiency} as a way to quantify partisan symmetry and partisan gerrymandering \cite{Stephanopolous & McGhee}.  Vote efficiency is a measure of how well a given vote applied towards improving political representation.  In the case that a voter's desired candidate wins, any vote beyond what is necessary to win (in the simple case, 50\% + 1 vote) is wasted.  In the case when a voter's desired candidate loses, all votes for the losing candidate are wasted. Redistricting plans seeking a partisan bias will lead to fewer wasted votes for the favored party, while increasing wasted votes for the disadvantaged party. \\

@@

\subsection{Redistricting Processes}
Another key aspect when discussing gerrymandering is the political processes involved in redistricting.  The Constitution provides states with the ability to create their own rules in how districts are drawn, with the provisions that states will ensure balanced district populations, and that districts are redrawn at least every 10 years \cite{LULAC v. Perry}.\\

@@

  The population moment of area was also simple to compute, since the TIGER/Line data approximates each district as a polygon.  Again, we ignored the issue of clipping to the coastline to avoid introducing more error.  Using census block population data, we also computed the population moment of inertia of each district.  We used the method described in Section~\ref{background} to deal with the limited granularity of the population data.

@@

  \subsection {Computing Voter Efficiency}
  We calculate voter efficiency using data from a variety of sources.  The US Census Data, along with the Harvard Election Data Archive presents a great resource for Federal Election results.  State-by-state elections are best sourced from the respective state agencies that govern the election, such as the Secretary of State's office or Board of Elections.  To calculate voter efficiency, we first go back to the definition of wasted votes.  This measure of voter efficiency will only analyze two-party, single-winner elections.  Thus, for a given party $p$, their opposing party $o$ and a given district $i$, the number of wasted votes  if party $p$ wins ($V_{p} > V_{o}$)  is given by 
    \[ V_{wpi} = V_{pi} - \frac{V_{pi}+V_{oi}}{2}\]

>>>>

\usepackage{fancyhdr,hyperref,setspace,booktabs,amsmath,multirow,mathpazo}
\usepackage[pdftex]{graphicx}
\usepackage[margin=1in,includehead,headheight=15pt]{geometry}

@@

  \section{Background}\label{s:background}

@@

  A given plan has symmetry if "similary-situated parties are treated equally", thus expecting that an even split in votes across two parties would have an even split in seats. Furthermore, if a plaintiff challenging a redistricting plan can demonstrate partisan intent and asymmetry, it would be sufficient for the burden of proof to shift to the state.  Nevertheless, while acknowledging the viability of symmetry as a metric to determine a discriminatory impact on voters, the court failed to establish an accepted standard or test to determine illegal gerrymandering.  Existing measures at the time, as calculated by social scientists, used hypothetical models to predict how election outcomes would turn out, given certain shifts in the electorate and certain vote shares in a given election. The court rejected the notion of using hypothetical models for a standard of constitutionality. \cite{LULAC} \\

  With this in mind,  as an alternative to other existing metrics, two legal scholars recently proposed measuring \textit{vote efficiency} as a way to quantify partisan symmetry and partisan gerrymandering \cite{stephanopoulos}.  Vote efficiency is a measure of how well a given vote applied towards improving political representation.  In the case that a voter's desired candidate wins, any vote beyond what is necessary to win (in the simple case, 50\% + 1 vote) is wasted.  In the case when a voter's desired candidate loses, all votes for the losing candidate are wasted. Redistricting plans seeking a partisan bias will lead to fewer wasted votes for the favored party, while increasing wasted votes for the disadvantaged party. \\

@@

\subsection{Redistricting Processes}
Another key aspect when discussing gerrymandering is the political processes involved in redistricting.  The Constitution provides states with the ability to create their own rules in how districts are drawn, with the provisions that states will ensure balanced district populations, and that districts are redrawn at least every 10 years \cite{LULAC}.\\

@@

  The population moment of area was also simple to compute, since the TIGER/Line data approximates each district as a polygon.  Again, we ignored the issue of clipping to the coastline to avoid introducing more error.  Using census block population data, we also computed the population moment of inertia of each district.  We used the method described in Section~\ref{s:background} to deal with the limited granularity of the population data.

@@

  \subsection {Computing Voter Efficiency}
  We calculate voter efficiency using data from a variety of sources.  The US Census Data, along with the Harvard Election Data Archive~\cite{heda} presents a great resource for Federal Election results.  State-by-state elections are best sourced from the respective state agencies that govern the election, such as the Secretary of State's office or Board of Elections.  To calculate voter efficiency, we first go back to the definition of wasted votes.  This measure of voter efficiency will only analyze two-party, single-winner elections.  Thus, for a given party $p$, their opposing party $o$ and a given district $i$, the number of wasted votes  if party $p$ wins ($V_{p} > V_{o}$)  is given by 
    \[ V_{wpi} = V_{pi} - \frac{V_{pi}+V_{oi}}{2}\]
